---
title: "Reading & Writing Data in R"
author: "YOUR NAME HERE"
date: 'Last rendered on `r format(Sys.time(), "%A, %B %d, %Y @ %I:%M %p")`'
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4
---

```{r globaloptions, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

```{r}
library(tidyverse)
library(readxl)
library(writexl)
library(jsonlite)
```

## "Whitespace" Files

### The `read_table()` Function

    # syntax
    read_table(
      file,
      col_names = TRUE,
      col_types = NULL,
      locale = default_locale(),
      na = "NA",
      skip = 0,
      n_max = Inf,
      guess_max = min(n_max, 1000),
      progress = show_progress(),
      comment = "",
      show_col_types = should_show_types(),
      skip_empty_rows = TRUE
    )

```{r}
# remember the script we saw in Week 1?

mlco2v1 <- read_table(
  file = "https://gml.noaa.gov/webdata/ccgg/trends/co2/co2_mm_mlo.txt",
  comment = "#",
  col_names = c(
    "year",
    "month",
    "dec_date",
    "co2",
    "co2_adj",
    "num_days",
    "sd_days",
    "uncertainty"
  )
)
```

```{r}
glimpse(mlco2v1)
```

```{r}
mlco2v2 <- read_table(
  file = "https://gml.noaa.gov/webdata/ccgg/trends/co2/co2_mm_mlo.txt",
  comment = "#",
  col_names = c(
    "year",
    "month",
    "dec_date",
    "co2",
    "co2_adj",
    "num_days",
    "sd_days",
    "uncertainty"
  ),
  col_types = "iinnnnnn"
)
```

```{r}
glimpse(mlco2v2)
```

## Delimited Files

### The `read_delim()` Function

    # syntax
    # general format
    read_delim(
      file,
      delim = NULL,
      quote = "\"",
      escape_backslash = FALSE,
      escape_double = TRUE,
      col_names = TRUE,
      col_types = NULL,
      col_select = NULL,
      id = NULL,
      locale = default_locale(),
      na = c("", "NA"),
      quoted_na = TRUE,
      comment = "",
      trim_ws = FALSE,
      skip = 0,
      n_max = Inf,
      guess_max = min(1000, n_max),
      name_repair = "unique",
      num_threads = readr_threads(),
      progress = show_progress(),
      show_col_types = should_show_types(),
      skip_empty_rows = TRUE,
      lazy = should_read_lazy()
    )

```{r}

```

### The `read_csv()` Function

    # comma separated values
    read_csv(
      file,
      col_names = TRUE,
      col_types = NULL,
      col_select = NULL,
      id = NULL,
      locale = default_locale(),
      na = c("", "NA"),
      quoted_na = TRUE,
      quote = "\"",
      comment = "",
      trim_ws = TRUE,
      skip = 0,
      n_max = Inf,
      guess_max = min(1000, n_max),
      name_repair = "unique",
      num_threads = readr_threads(),
      progress = show_progress(),
      show_col_types = should_show_types(),
      skip_empty_rows = TRUE,
      lazy = should_read_lazy()
    )

```{r}

```

### The `read_tsv()` Function

    # tab-separated values
    read_tsv(
      file,
      col_names = TRUE,
      col_types = NULL,
      col_select = NULL,
      id = NULL,
      locale = default_locale(),
      na = c("", "NA"),
      quoted_na = TRUE,
      quote = "\"",
      comment = "",
      trim_ws = TRUE,
      skip = 0,
      n_max = Inf,
      guess_max = min(1000, n_max),
      progress = show_progress(),
     name_repair = "unique",
      num_threads = readr_threads(),
      show_col_types = should_show_types(),
      skip_empty_rows = TRUE,
      lazy = should_read_lazy()
    )

```{r}

```

## RDS and RDATA Files

### Reading and Writing `.rds`

An `.rds` file is an `R`-specific file type that stores a single `R` object, such as a vector, list, dataset, plot, or function. 

Read an object from an `.rds` file using the following general code. You may need to specify a path name. You can also read data directly from a URL.

```{r, readrds, eval = FALSE}
readRDS(file = "my_data.rds")
```

    # syntax
    readRDS(
      file, 
      refhook = NULL
    )

```{r}

```

Save a single object to an `.rds` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder.

```{r, saverds, eval = FALSE}
saveRDS(objectname, file = "my_data.rds")
```

    # syntax
    saveRDS(
      object, 
      file = "", 
      ascii = FALSE, 
      version = NULL,
      compress = TRUE, 
      refhook = NULL
    )

```{r}

```

### Reading and Writing `.Rdata`

An `.Rdata` file is an `R`-specific file type that stores multiple `R` objects together in a single file. It is sometimes abbreviated as `.Rda`.

Load an `.Rdata` file using the following general code. You may need to specify a path name. You can also read data directly from a URL.

```{r, loadrata, eval = FALSE}
load("data.RData")
```

    # syntax
    load(
      file, 
      envir = parent.frame(), 
      verbose = FALSE
    )

```{r}

```

Save a one or more objects to an `.Rdata` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder.

```{r, saverdata1, eval = FALSE}
save(objectname, file = "data.RData")
```

```{r, saverdata2, eval = FALSE}
save(objectname1, objectname2, file = "data.RData")
```

    # syntax
    save(..., 
      list = character(),
      file = stop("'file' must be specified"),
      ascii = FALSE, 
      version = NULL, 
      envir = parent.frame(),
      compress = isTRUE(!ascii), 
      compression_level,
      eval.promises = TRUE, 
      precheck = TRUE
    )

```{r}

```

Save your entire workspace (all objects in your Environment) to an `.Rdata` file using the following general code. If the data are being saved to a folder you need to specify the path to the folder. It can be reloaded with the `load()` function.

```{r, savewkspc, eval = FALSE}
save.image("myworkspace.RData")
```

    # syntax
    save.image(
      file = ".RData", 
      version = NULL, 
      ascii = FALSE,
      compress = !ascii, 
      safe = TRUE
    )

```{r}

```

## Excel Files

### Workbook Format

    # syntax
    excel_format(guess = TRUE)

```{r}

```

### Number of Sheets

    # syntax
    excel_sheets(path)
    
```{r}

```

### Read a Workbook Sheet

    # general syntax, guesses file type
    read_excel(
      path,
      sheet = NULL,
      range = NULL,
      col_names = TRUE,
      col_types = NULL,
      na = "",
      trim_ws = TRUE,
      skip = 0,
      n_max = Inf,
      guess_max = min(1000, n_max),
      progress = readxl_progress(),
      .name_repair = "unique"
    )

    # if you know it is an .xlsx file
    read_xlsx(
      path,
      sheet = NULL,
      range = NULL,
      col_names = TRUE,
      col_types = NULL,
      na = "",
      trim_ws = TRUE,
      skip = 0,
      n_max = Inf,
      guess_max = min(1000, n_max),
      progress = readxl_progress(),
      .name_repair = "unique"
    )
    
```{r}

```

### Write to an Excel File

    # syntax
    write_xlsx(
      x,
      path = tempfile(fileext = ".xlsx"),
      col_names = TRUE,
      format_headers = TRUE,
      use_zip64 = FALSE
    )
    
```{r}

```

## JSON Files

### TBA

<hr>
```{r}
sessionInfo()
```
